Title

### 2023-05-14 main.tex
Algunas correcciones

We can also see how an arbitrary Pauli channel acts on an arbitrary  
density matrix.
To do it, we substitute eq. (\ref{eq: Density Matrix}) 
in eq. (\ref{eq: Pauli channel 1 qbit}):
\begin{equation}
\mathcal{E}(\rho) = \dfrac{1}{2}\sum_{\gamma,\alpha=0}^3 k_{\gamma} r_{\alpha} \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}.
\end{equation}
This can be simplified by using the following property of Pauli matrices:
\begin{equation}
\label{eq: propiedad-pauli}
\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A_{\alpha,\gamma} = \begin{pmatrix}
1 & 1 & 1 & 1\\
1 & 1 & -1 &-1 \\
1 & -1 & 1 & -1 \\
1 & -1 & -1 & 1
\end{pmatrix},
\end{equation}
which leads to
\begin{equation}
\label{eq: rho-transformada}
\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
\end{equation}
Eq.~(\ref{eq: rho-transformada}) once again has the form of eq.~(\ref{eq: Density Matrix})
but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
This gives us another way of understanding Pauli channels
as operations that take each component $r_{\alpha}$
of the density matrix and multiplies them
by $\sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}$, 
that is:
\begin{equation}
\label{eq: multipliers}
r_{\alpha}  \xrightarrow[\text{Channel}]{\text{Pauli}}  \tau_{\alpha} r_{\alpha} ,\;\; \tau_{\alpha} := \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}.
\end{equation}
Notice that $\tau_0 = 1$, which is a consequence of $\sum_{\gamma}k_{\gamma}=1$
and ensures that after the channel, the resulting density matrix still has trace one. 
Furthermore, reverting the definition of $\tau_{\alpha}$ by using that $A^{-1} = \dfrac{1}{4} A$, 
we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\alpha} A_{\alpha,\gamma} \tau_{\alpha}$.
Then, using that $k_{\gamma} \geq 0$
we get the following conditions on the multipliers $\tau_{\alpha}$:
\begin{eqnarray}
\label{eq: conditions-tetrahedron}
&1+\tau_i -\tau_j - \tau_k \geq 0,  \;\;\; \text{for $i,j,k$ different numbers in $\{1,2,3\}$}, \\
&1+\tau_1 + \tau_2 + \tau_3 \geq 0.
\end{eqnarray}

@@

As in the one qubit case, Pauli channels for $N$ qubits 
attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
This can be seen by substituting eq. (\ref{eq:  Density matrix Nqbit}) in eq. (\ref{eq: pauli channel N-qubit})
and using the property of eq. (\ref{eq: propiedad-pauli}):
\begin{align*}
\mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
\end{align*}
which means that applying the Pauli channel multiplies the 
components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
% }}}
\subsection{Pauli Dynamical Maps} % {{{
\label{subsec: Pauli Dynamical Maps}

@@

% To design the circuit, we recall that a Pauli channel, as the one in
% eq.~(\ref{eq: pauli channel N-qubit}), applies each Pauli operator
% $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
% Given this, it is easy to construct a quantum circuit that implements 
% a Pauli channel with the help of $2N$ ancilla qubits,
% see \fref{fig: circuit-pauli}.
% The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
% \begin{eqnarray}
% \label{eq: state0}
% \sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
% \end{eqnarray}
% in the ancilla qubits, 
% where $b_{\vec{\gamma}}$ are numbers such that $
% |b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
% The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined as $|\gamma_1 \rangle
% \cdots |\gamma_N\rangle$.

@@

The first part of the circuit involves the creation of the state
\begin{eqnarray}
\label{eq: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
\cdots |\gamma_N\rangle$.
% \cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
% de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
% Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
When measured in the computational basis, the state given in eq.~(\ref{eq: state})
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
The circuit in fig.~(\ref{fig: circuit-pauli}) uses this fact
to apply $\sigma_{\vec{\gamma}}$ on the main qubits
with a probability $k_{\vec\gamma}$ by using controlled operations 
conditioned on the state of the system being $|\vec{\gamma}\rangle$,
just as the Pauli channel is supposed to do.  
% 
% that apply $\sigma_{\vec{\gamma}}$ to the main qubits
% only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
% 
% Therefore, the circuit from fig.~(\ref{fig: circuit-pauli}) 
% applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
% with a probability $k_{\vec{\gamma}}$, 
% just as a Pauli channel is supposed to do.

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in fig.~\ref{fig: circuit-pauli-1},
which is a special case of fig. \ref{fig: circuit-pauli}
but with all details  explicitly shown.

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{
% \cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho.} \tbnote{Va, lo hice así, espero haberlo hecho bien.} \cpnote{ 
% Otra cosa quizá para discutir.  La creacion del estado especial de dos qubits no esta
% aca explicita. Eso creo que si lo podemos hacer en general, o no? Como sería eso? Lo discutimos
% a ver si lo pones?} \tbnote{Sí. En la figura que está ahora lo puse (antes sólo había un bloque que
%  decía que se crea el estado $|b\rangle$ sobre los qubits de ancilla).
% Ahora que lo pienso, sí lo prefiero así con la creación explícita y creo que mejora a la discusión después,
% porque muestra que en general se necesitan tres ángulos y es lo que luego buscamos 
% reducir a sólo uno}
\cpnote{No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
el lugar apropiado en el texto}
{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of Fig~(\ref{fig: circuit-pauli}).  Here we have two
ancilla qubits, and the state $b_{00} |00\rangle + b_{01} |01\rangle + b_{10}
|10\rangle + b_{11}|11\rangle$ is created on them with the help of three
rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, $ \theta_1 = 2 \arccos(\sqrt{k_{00} +
k_{01}})$ and $ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$. }
\label{fig: circuit-pauli-1} 
\end{figure} % }}}

Using the quantum computers that IBM has available~\cite{Qiskit}, we sampled
$249$ one-qubit Pauli channels and simulated them using the ibmq-lima quantum
computer.  For each of these channels, we used quantum process
tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit.  Then, we compared this {\color{red}
Choi matrix} {\color{orange} operator} with the theoretical {\color{red} Choi
matrix $\mathcal{C}_T$} {\color{orange} operator $\xi_T$} of the channel we
wanted to implement.  \cpnote{Quizá referirnos mejor al canal? Lo discutimos.}
\tbnote{Ah sí, mejor. Cambié lo que puse en rojo por lo que está en naranja.}

We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
with the probability that one can distinguish two channels \cpnote{Revisa esta 
frase a ver si te parece}.
% To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
% which gives us a method of discriminating \cpnote{no solo discrimina... todas
% las normas lo hacen, pero nos permite ver que tan parecidos son dos canales. 
% Es como la fidelidad. Itera.} between quantum channels \cpnote{Tambien esta frase
% no conecta bien con lo que sigue}.
In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
with probability $1/2$ each,
and tries to guess which channel they received
by applying it to a state $\rho$ and measuring the result.
Then, the maximal probability of success (out of all possible states $\rho$) that
the agent guesses correctly is~\cite{Benenti}:
\begin{equation}
\label{eq: probability-success}
p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
\end{equation}
where $|| \cdot ||_{\diamond}$ is the diamond norm \cpnote{no la hemos 
definido matemáticamente}.  
% Notice that $p_{\succ}=1/2$
% means that the channels are the same \cpnote{qioza una frase explicando porque
% esto es razonable}
% \tbnote{Cambiar la oración pasada por:} {\color{orange} 
Notice that if the channels are the same, then $p_{\succ}=1/2$. 
This is expected because in this situation the agent
has no way of distinguishing the channels and has no choice but to completely
guess, which results in a probability of success of $1/2$.
On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
distinguishable.
% \cpnote{hummm ejemplo al menos para nosotros.} 
% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
% (para $i\neq j$), se cumple esto.
% También quería ejemplos no unitarios, pero no encontré.}

Finally, using the representation of Pauli channels in a tetrahedron as
in eq.~(\ref{eq: conditions-tetrahedron}),
we show in fig.~(\ref{fig: fidelity one qubit}) the maximal probabilities of
success defined by eq. (\ref{eq: probability-success}) for the channels
analyzed. 
We can see that channels close to the 
completely depolarizing
channel (that is close to the center of the tetrahedron)
have a low $p_{\succ}$, while those 
close to unitary channels have much higher $p_{\succ}$.
This means that channels closer to the 
completely depolarizing channel are simulated better on the quantum computers.
This is reasonable because quantum computers are prone to errors
that depolarize qubits, which isn't very problematic
when trying to simulate depolarization but it is 
when simulating unitary processes.
\cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
figuras y mas inspiracion}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{probabilities-points.png}\\
\caption{{\bf Maximal probabilities of success for one-qubit Pauli channel}
$p_{\succ}$ of one-qubit Pauli channels implemented on IBM's ibmq-lima. The
channels are plotted in the tetrahedron of Pauli channels, with a color bar
indicating the distinguishability of each channel's implementation using the
circuit for a 1-qubit Pauli channel. \cpnote{Poner la barra del tamaño apropiado 
y quizá juntar con los cortes que tenemos. Discutir en vivo con Tomas a ver que onda. 
Tambien poner mas puntos experimentales.}}
\label{fig: fidelity one qubit}
\end{figure}

\newpage
\tbnote{Algunas paletas de colores diferentes:}

\begin{figure}
\centering
\includegraphics[width=.32\columnwidth]{images/tetra-col1.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col2.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col3.png} \\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col4.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col5.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col6.png}\\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col7.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col8.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col9.png}\\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col10.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col11.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col12.png}\\[1ex]
\includegraphics[width=.32\columnwidth]{images/tetra-col13.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col14.png}
\includegraphics[width=.32\columnwidth]{images/tetra-col16.png}\\[1ex]
\caption{Algunos colores posibles. Creo qeu me gustaria usar otra candidad, 
como la fidelidad, pero definida a partir de la norma diamante. 
Asi, 1 es perfecto y 0 esta mal. De estas, me gusta la de abajo 
a la izquiera porque siento que distingue bien, pero si toca entnoces
usar los mismos colores en la fig 5. Te propongo dejar un tetraedro y los
cinco cortes para que nos quede algo de 3 columnsas y dos filas. 
propongo tambien que se ponta la leyenda en la figura y no encima. 
Si te haces bolas con las figuras, discutimos como hacerlas en TIKZ.  }
\end{figure}

\begin{figure}
\centering
\begin{subfigure}{.9\textwidth}
\centering
\includegraphics[width=.30\columnwidth]{images/corte1.png}
\includegraphics[width=.30\columnwidth]{images/corte2.png}
\includegraphics[width=.30\columnwidth]{images/corte3.png} \\[1ex]
\includegraphics[width=.30\columnwidth]{images/corte4.png}
\includegraphics[width=.30\columnwidth]{images/corte5.png}
\end{subfigure}%
\begin{subfigure}{0.1\textwidth}
\includegraphics[width=.8\columnwidth]{images/col.png}\\[1ex]
\end{subfigure}
\caption{\tbnote{Aquí hay algunos cortes de la figura anterior.
De qué forma lo agrego a la figura anterior?}}
\end{figure}

% }}}
% }}}
\section{OPR Circuits} % {{{
\label{sec: OPR Circuits}
\cpnote{Quizá abrir con un parrafo de motivacion. Quizá lo tenemos que hablar. }
\cpnote{No se sabe aun que son OPR circuits. Poner completo}

Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
of fig.~(\ref{fig: circuit-pauli}). However, there is one difference: 
the state to be created on the ancilla qubits now 
depends on a parameter $p$, and it is represented by the expression:
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
Thus, we temporarily shift our focus from Pauli
channels and dynamical maps to the general problem of 
creating a circuit to generate a curve of
states like the one described in \eref{eq: parametrized state}.
\cpnote{me gusta mas usar el comando eref para que si toca cambiarlo, dependiendo 
de la revista, lo pueda hacer de un solo jalon. Lo mismo para las 
figuras.}

In general, producing this curve of states will require multiple rotations
parametrized by $p$. For instance, in the case of a two-qubit curve of states,
we would typically need three rotations that depend on $p$, similar to those
illustrated for the ancilla qubits in \fref{fig: circuit-pauli-1}.
Moreover, creating an $N$-qubit curve of states
usually necessitates $N-1$ parametrized rotations.
\cpnote{no me salen esas cuentas.}

>>>>

We can also see how an arbitrary Pauli channel acts on an arbitrary  
density matrix.
To do it, we substitute \eref{eq: Density Matrix} 
in \eref{eq: Pauli channel 1 qbit}:
\begin{equation}
\mathcal{E}(\rho) = \dfrac{1}{2}\sum_{\gamma,\alpha=0}^3 k_{\gamma} r_{\alpha} \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}.
\end{equation}
This can be simplified by using the following property of Pauli matrices:
\begin{equation}
\label{eq: propiedad-pauli}
\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A_{\alpha,\gamma} = \begin{pmatrix}
1 & 1 & 1 & 1\\
1 & 1 & -1 &-1 \\
1 & -1 & 1 & -1 \\
1 & -1 & -1 & 1
\end{pmatrix},
\end{equation}
which leads to
\begin{equation}
\label{eq: rho-transformada}
\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
\end{equation}
\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix}
but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
This gives us another way of understanding Pauli channels
as operations that take each component $r_{\alpha}$
of the density matrix and multiplies them
by $\sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}$, 
that is:
\begin{equation}
\label{eq: multipliers}
r_{\alpha}  \xrightarrow[\text{Channel}]{\text{Pauli}}  \tau_{\alpha} r_{\alpha} ,\;\; \tau_{\alpha} := \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}.
\end{equation}
Notice that $\tau_0 = 1$, which is a consequence of $\sum_{\gamma}k_{\gamma}=1$
and ensures that after the channel, the resulting density matrix still has trace one. 
Furthermore, reverting the definition of $\tau_{\alpha}$ by using that $A^{-1} = \dfrac{1}{4} A$, 
we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\alpha} A_{\alpha,\gamma} \tau_{\alpha}$.
Then, using that $k_{\gamma} \geq 0$
we get the following conditions on the multipliers $\tau_{\alpha}$:
\begin{eqnarray}
\label{eq: conditions-tetrahedron}
&1+\tau_i -\tau_j - \tau_k \geq 0,  \;\;\; \text{for $i,j,k$ different numbers in $\{1,2,3\}$}, \\
&1+\tau_1 + \tau_2 + \tau_3 \geq 0.
\end{eqnarray}

@@

As in the one qubit case, Pauli channels for $N$ qubits 
attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
This can be seen by substituting \eref{eq:  Density matrix Nqbit} in \eref{eq: pauli channel N-qubit}
and using the property of \eref{eq: propiedad-pauli}:
\begin{align*}
\mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
\end{align*}
which means that applying the Pauli channel multiplies the 
components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
% }}}
\subsection{Pauli Dynamical Maps} % {{{
\label{subsec: Pauli Dynamical Maps}

@@

% To design the circuit, we recall that a Pauli channel, as the one in
% \eref{eq: pauli channel N-qubit}, applies each Pauli operator
% $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
% Given this, it is easy to construct a quantum circuit that implements 
% a Pauli channel with the help of $2N$ ancilla qubits,
% see \fref{fig: circuit-pauli}.
% The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
% \begin{eqnarray}
% \label{eq: state0}
% \sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
% \end{eqnarray}
% in the ancilla qubits, 
% where $b_{\vec{\gamma}}$ are numbers such that $
% |b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
% The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined as $|\gamma_1 \rangle
% \cdots |\gamma_N\rangle$.

@@

The first part of the circuit involves the creation of the state
\begin{eqnarray}
\label{eq: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
\cdots |\gamma_N\rangle$.
% \cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
% de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
% Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
When measured in the computational basis, the state given in \eref{eq: state}
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
The circuit in \fref{fig: circuit-pauli} uses this fact
to apply $\sigma_{\vec{\gamma}}$ on the main qubits
with a probability $k_{\vec\gamma}$ by using controlled operations 
conditioned on the state of the system being $|\vec{\gamma}\rangle$,
just as the Pauli channel is supposed to do.  
% 
% that apply $\sigma_{\vec{\gamma}}$ to the main qubits
% only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
% 
% Therefore, the circuit from \fref{fig: circuit-pauli} 
% applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
% with a probability $k_{\vec{\gamma}}$, 
% just as a Pauli channel is supposed to do.

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the state 
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}})
\label{eq:angle2} \\
\theta_2 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{
\cpnote{No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
el lugar apropiado en el texto} \tbnote{Lo pasé al texto}
{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of \fref{fig: circuit-pauli}.  Here we have two
ancilla qubits and we use three rotations
of angles given by \eref{eq:angle} to create the state $\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
on them.
%and the state $b_{00} |00\rangle + b_{01} |01\rangle + b_{10}
%|10\rangle + b_{11}|11\rangle$ is created on them with the help of three
%rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, $ \theta_1 = 2 \arccos(\sqrt{k_{00} +
%k_{01}})$ and $ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$.
}
\label{fig: circuit-pauli-1} 
\end{figure} % }}}

Using the quantum computers that IBM has available~\cite{Qiskit}, we sampled
one-qubit Pauli channels and simulated them using the ibmq-lima quantum
computer.  For each of these channels, we used quantum process
tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit.  Then, we compared this {\color{red}
Choi matrix} {\color{orange} operator} with the theoretical {\color{red} Choi
matrix $\mathcal{C}_T$} {\color{orange} operator $\xi_T$} of the channel we
wanted to implement.  \cpnote{Quizá referirnos mejor al canal? Lo discutimos.}
\tbnote{Ah sí, mejor. Cambié lo que puse en rojo por lo que está en naranja.}

We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
with the probability that one can distinguish two channels \cpnote{Revisa esta 
frase a ver si te parece} 
\tbnote{Sí, perfecto}.
% To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
% which gives us a method of discriminating \cpnote{no solo discrimina... todas
% las normas lo hacen, pero nos permite ver que tan parecidos son dos canales. 
% Es como la fidelidad. Itera.} between quantum channels \cpnote{Tambien esta frase
% no conecta bien con lo que sigue}.
In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
with probability $1/2$ each,
and tries to guess which channel they received
by applying it to a state $\rho$ and measuring the result.
Then, the maximal probability of success (out of all possible states $\rho$) that
the agent guesses correctly is~\cite{Benenti}:
\begin{equation}
\label{eq: probability-success}
p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
\end{equation}
where $|| \cdot ||_{\diamond}$ is the diamond norm \cpnote{no la hemos 
definido matemáticamente} \tbnote{Qué tal así:} {\color{orange}, defined by 
\begin{align*}
||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
\end{align*}
with $I$ the identity map,
$|| \cdot ||_1$ the trace norm and the maximization
done over all density matrices $\rho$.}

Notice that if the channels are the same, then $p_{\succ}=1/2$. 
This is expected because in this situation the agent
has no way of distinguishing the channels and has no choice but to completely
guess, which results in a probability of success of $1/2$.
On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
distinguishable.
% \cpnote{hummm ejemplo al menos para nosotros.} 
% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
% (para $i\neq j$), se cumple esto.
% También quería ejemplos no unitarios, pero no encontré.}

Finally, using the representation of Pauli channels in a tetrahedron as
in \eref{eq: conditions-tetrahedron},
we show in \fref{fig: fidelity one qubit} the maximal probabilities of
success defined by \eref{eq: probability-success} for the channels
analyzed. 
We can see that channels close to the 
completely depolarizing
channel (that is close to the center of the tetrahedron)
have a low $p_{\succ}$, while those 
close to unitary channels have much higher $p_{\succ}$.
This means that channels closer to the 
completely depolarizing channel are simulated better on the quantum computers.
This is reasonable because quantum computers are prone to errors
that depolarize qubits, which isn't very problematic
when trying to simulate depolarization but it is 
when simulating unitary processes.
\cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
figuras y mas inspiracion}
\tbnote{Va}

@@

\begin{figure}
\centering
\includegraphics[width=0.55\textwidth]{images/probabilities-points.png}\\
\caption{{\bf Maximal probabilities of success for one-qubit Pauli channel}
$p_{\succ}$ of one-qubit Pauli channels implemented on IBM's ibmq-lima. The
channels are plotted in the tetrahedron of Pauli channels, with a color bar
indicating the distinguishability of each channel's implementation using the
circuit for a 1-qubit Pauli channel. \cpnote{Poner la barra del tamaño apropiado 
y quizá juntar con los cortes que tenemos. Discutir en vivo con Tomas a ver que onda. 
Tambien poner mas puntos experimentales.} \tbnote{Cambié lo de la barra y puse más puntos experimentales en los cortes que están en 
la figura más abajo
(no en esta figura porque ya se llena mucho de puntos).}
\cpnote{ Creo qeu me gustaria usar otra candidad, 
como la fidelidad, pero definida a partir de la norma diamante. 
Asi, 1 es perfecto y 0 esta mal.} \tbnote{Lo que se me ocurre es algo como $2*(1-p_{succ})$ que justo cumple eso y en términos
de la norma es $1-1/2||\xi_I - \xi_T||_{\diamond}$} \cpnote{ De estas, me gusta la de abajo 
a la izquiera porque siento que distingue bien, pero si toca entnoces
usar los mismos colores en la fig 5.} \tbnote{Ya agarré esos colores} \cpnote{Te propongo dejar un tetraedro y los
cinco cortes para que nos quede algo de 3 columnsas y dos filas. 
propongo tambien que se ponta la leyenda en la figura y no encima. 
Si te haces bolas con las figuras, discutimos como hacerlas en TIKZ. } \tbnote{Lo puse en la figura siguiente. Poniéndolo con 3 columnas y dos filas queda
muy chiquita la figura del tetraedro y no se llega a ver nada, así que lo puse grande y los cortes
alrededor. }}
\label{fig: fidelity one qubit}
\end{figure}

%
%\begin{figure}
%\centering
%\includegraphics[width=.32\columnwidth]{images/tetra-col1.png}
%\includegraphics[width=.32\columnwidth]{images/tetra-col2.png}
%\includegraphics[width=.32\columnwidth]{images/tetra-col3.png} \\[1ex]
%\includegraphics[width=.32\columnwidth]{images/tetra-col4.png}
%\includegraphics[width=.32\columnwidth]{images/tetra-col5.png}
%\includegraphics[width=.32\columnwidth]{images/tetra-col6.png}\\[1ex]
%\includegraphics[width=.32\columnwidth]{images/tetra-col7.png}
%\includegraphics[width=.32\columnwidth]{images/tetra-col8.png}
%\includegraphics[width=.32\columnwidth]{images/tetra-col9.png}\\[1ex]
%\includegraphics[width=.32\columnwidth]{images/tetra-col10.png}
%\includegraphics[width=.32\columnwidth]{images/tetra-col11.png}
%\includegraphics[width=.32\columnwidth]{images/tetra-col12.png}\\[1ex]
%\includegraphics[width=.32\columnwidth]{images/tetra-col13.png}
%\includegraphics[width=.32\columnwidth]{images/tetra-col14.png}
%\includegraphics[width=.32\columnwidth]{images/tetra-col16.png}\\[1ex]
%\caption{Algunos colores posibles. \cpnote{ Creo qeu me gustaria usar otra candidad, 
%como la fidelidad, pero definida a partir de la norma diamante. 
%Asi, 1 es perfecto y 0 esta mal.} \tbnote{Algo como } \cpnote{ De estas, me gusta la de abajo 
%a la izquiera porque siento que distingue bien, pero si toca entnoces
%usar los mismos colores en la fig 5. Te propongo dejar un tetraedro y los
%cinco cortes para que nos quede algo de 3 columnsas y dos filas. 
%propongo tambien que se ponta la leyenda en la figura y no encima. 
%Si te haces bolas con las figuras, discutimos como hacerlas en TIKZ. } }
%\end{figure}
